This section will contain an explanation of the methodology taken to evaluate different approaches to Multi Day Trip
Planning.
This explanation will include a description of the approaches to be evaluated, alongside the experiment procedure used
and any constraints that were placed on the problem.
Later in this section, the results of these experiments will be presented and discussed.

\subsection{Methodology}\label{subsec:evaluation-methodology}
The purpose of this evaluation is to compare the performance of different approaches to Multi Day Trip Planning.
The experimental process aimed to answer the following questions:
\begin{itemize}
    \item How do the different approaches compare in terms of computation time?
    \item How do the different approaches compare in terms of the quality of trips produced?
    \item How does the performance of each approach scale with input complexity?
\end{itemize}
To answer these questions, each proposed approach will be applied to a range of different inputs, recording the
computation time to produce a trip and the quality of the trip produced according to the cost function described in
section~\ref{subsec:objective-function}.

\noindent
For use in these experiments 25 testing data sets were created, each representing inputs for trips to major cities
around the world.
Each data set includes:
\begin{itemize}
    \item A set of coordinates, representing different points of interest around the city.
    \item A list of durations, representing the time to be spent at each point of interest.
    \item A complete graph, containing the time taken to travel between each point of interest.
\end{itemize}
These were created using openrouteservice, the process of which was previously described in
section~\ref{subsubsec:input-generation} titled ``Input Generation''.
Due to previously discussed limitations of the openrouteservice API, each dataset was limited to 25 points of
interest.\\

\noindent
To investigate how the performance of these algorithms scales with input complexity, experiments with a range of
inputs for the number of locations and number of days in each trip were conducted.
For these experiments, a subset of locations and their corresponding durations and graphs were selected from the 25
datasets, each approach was run on the same subset.
Every approach was run on every dataset for every combination of locations and days.
A full list of the combinations of the number of locations and number of days is available in table~\ref{tab:locations-and-days}.
\begin{table}[H]
    \centering
    \caption{Lists all combinations of the number of locations and number of days used in evaluation.}\label{tab:locations-and-days}
    \begin{tabular}{ r | l }
        Number of & Number of \\
        Locations & Days \\
        25 & 7, 6, 5, 4 \\
        20 & 6, 5, 4, 3 \\
        15 & 5, 4, 3, 2 \\
        10 & 4, 3, 2 \\
        8  & 3, 2 \\
        5  & 2 \\
    \end{tabular}
\end{table}

\noindent
Using various combinations of the implemented clustering, routing and trip generation algorithms, a total of 16
approaches were evaluated.
The full list of these approaches and an explanation of each one, as well as the shorthand used to refer to each
approach, is available in table~\ref{tab:approaches}.
Most of these approaches are either trip generation methods, or different combinations of the clustering and routing
algorithms previously described.
The only exceptions to this are the `Genetic Algorithm Clustering + Greedy Routing + Brute Force' (GAC+GR+BF) and
`Genetic Algorithm Centroid Clustering + Greedy Routing + Brute Force' (GACC+GR+BF) approaches.
These approaches use greedy routing to evaluate the clusters found during the genetic algorithm process.
Then, once evolution has completed, the resultant clusters are passed to Brute Force to find optimal routes within
the clusters found.
The hope is that greedy routing will allow a fast genetic algorithm, while using Brute Force will allow for an
optimal final trip.

\begin{center}
    \caption{Lists and describes all approaches evaluated.}\label{tab:approaches}
    \footnotesize
    \begin{longtable}[H]{| p{6cm} | p{9cm} |}
        \hline
        Approach & Description \\
        \hline
        Genetic Algorithm Trip Generation (GATG) & Generates trip using Genetic Algorithm \\
        \hline
        Greedy Insertion Trip Generation (GITG) & Generates trip using Greedy Insertion \\
        \hline
        K-Means Clustering + Greedy Routing (KM+GR) & Finds clusters using K-Means then finds intra-cluster routes
        Greedy Routing \\
        \hline
        K-Means Clustering + Greedy Insertion (KM+GI) & Finds clusters using K-Means then finds intra-cluster routes
        using Greedy Insertion Routing \\
        \hline
        K-Means Clustering + Brute Force (KM+BF) & Finds clusters using K-Means then finds intra-cluster routes using
        Brute Force Routing \\
        \hline
        K-Means Clustering + Convex Hull (KM+CH) & Finds clusters using K-Means then finds intra-cluster routes using
        Convex Hull Routing \\
        \hline
        K-Means Clustering + Genetic Algorithm Routing (KM+GAR) & Finds clusters using K-Means then finds intra-cluster
        routes using Genetic Algorithm Routing \\
        \hline
        Genetic Algorithm Clustering + Greedy Routing (GAC+GR) & Finds clusters using Genetic Clustering then finds
        intra-cluster routes using Greedy Routing \\
        \hline
        Genetic Algorithm Clustering + Greedy Routing + Brute Force (GAC+GR+BF) & Finds clusters using Genetic
        Clustering then finds intra-cluster routes using Greedy Routing - Once final clusters are obtained,
        Brute Force is used to find final routes \\
        \hline
        Genetic Algorithm Clustering + Greedy Insertion (GAC+GI) & Finds clusters using Genetic Clustering then
        finds intra-cluster routes using Greedy Insertion \\
        \hline
        Genetic Algorithm Centroid Clustering + Greedy Routing (GACC+GR) & Finds clusters using Genetic Centroid
        Clustering then finds intra-cluster routes using Greedy Routing \\
        \hline
        Genetic Algorithm Centroid Clustering + Greedy Routing + Brute Force (GACC+GR+BF) & Finds clusters using Genetic
        Centroid Clustering then finds intra-cluster routes using Greedy Routing - Once final clusters are obtained,
        Brute Force is used to find final routes \\
        \hline
        Genetic Algorithm Centroid Clustering + Greedy Insertion (GACC+GI) & Finds clusters using Genetic Centroid
        Clustering then finds intra-cluster routes using Greedy Insertion Routing \\
        \hline
        Greedy Routing + Greedy Insertion (GR+GI) & Finds route using Greedy Routing then splits route into a multi-day
        trip using Greedy Insertion \\
        \hline
        Convex Hull + Greedy Insertion (CH+GI) & Finds route using Convex Hull Routing then splits route into a
        multi-day trip using Greedy Insertion \\
        \hline
        Genetic Algorithm Routing + Greedy Insertion (GAR+GI) & Finds route using Genetic Algorithm Routing then splits
        route into a multi-day trip using Greedy Insertion \\
        \hline
    \end{longtable}
\end{center}

During these experiments, genetic algorithms all shared the following hyperparameters:
\begin{itemize}
    \item Number of Generations: 150,
    \item Population Size: 50,
    \item Crossover Rate: 0.9.
\end{itemize}
Genetic Clustering approaches used a mutation rate of 0.1, while Genetic Routing approaches used a mutation rate of 0.4.

\subsection{Results \& Analysis}\label{subsec:results-and-analysis}
Through this experimentation each of the 25 datasets were tested using each combination of locations and days,
resulting in a total of 450 inputs given to each approach.
The average results of tests ran for several different combinations of locations and days are shown in
tables~\ref{tab:averages-8-locations-3-days} (8 locations and 3 days),
~\ref{tab:averages-15-locations-4-days} (15 locations and 4 days)
and~\ref{tab:averages-25-locations-7-days} (25 locations and 7 days).
The computation time and evaluation shown for each approach is the average of values obtained from all datasets ran
with these location and day inputs.
Also included are the standard deviation ($\sigma$), which represents the deviation in results between different
location data sets, and the coefficient of variation ($\frac{\sigma}{\mu}$), which represents the ratio between mean
values and their standard deviation.
The results are sorted by evaluation, and the best and worst values in each row are highlighted in bold and italic
respectively.
Table~\ref{tab:averages-all-tests} shows average results across all data sets and input sizes.
\begin{table}[H]
    \centering
    \caption{Lists average computation time and evaluation for each approach across tests using 8 locations and 3 days. This table also includes evaluations for Brute Force Trip Generation (BFTG) and Brute Force + Greedy Insertion (BF+GI)}\label{tab:averages-8-locations-3-days}
    \scriptsize
    \begin{tabular}{lllllll}
        Approach   & Computation  & Computation & Computation & Evaluation - $\mu$ & Evaluation - $\sigma$ & Evaluation - $\frac{\sigma}{\mu}$ \\
                   & Time - $\mu$ & Time - $\sigma$ & Time - $\frac{\sigma}{\mu}$ & & & \\
        BFTG       & \textit{10.963727}                                                  & \textit{1.373076}                                                     & 0.125238083                                                                        & \textbf{580.843119} & \textbf{145.607101}   & 0.25068232                        \\
        GAC+GR+BF  & 2.652661                                                            & 0.924027                                                              & 0.348339523                                                                        & 581.771109          & 147.287947            & 0.253171643                       \\
        GATG       & 0.828975                                                            & 0.470336                                                              & 0.56737038                                                                         & 582.483376          & 146.081298            & 0.250790502                       \\
        GAC+GR     & 2.652392                                                            & 0.924045                                                              & 0.348381659                                                                        & 583.209066          & 148.632858            & 0.254853476                       \\
        GACC+GR+BF & 1.901471                                                            & 0.515371                                                              & 0.271037872                                                                        & 592.071590          & 146.909233            & 0.248127482                       \\
        GACC+GR    & 1.901226                                                            & 0.515358                                                              & 0.271065947                                                                        & 593.390534          & 148.322398            & 0.249957472                       \\
        GAR+GI     & 0.691986                                                            & 0.224216                                                              & 0.324017778                                                                        & 650.987103          & 158.635774            & 0.243684972                       \\
        BF+GI      & 0.300547                                                            & 0.055220                                                              & 0.183732569                                                                        & 651.094458          & 160.621126            & 0.246694046                       \\
        CH+GI      & 0.003120                                                            & 0.004787                                                              & \textit{1.534394689}                                                               & 657.864674          & 157.007055            & 0.238661629                       \\
        GITG       & 0.004070                                                            & 0.004507                                                              & 1.107453904                                                                        & 661.532642          & 173.934502            & 0.26292656                        \\
        GR+GI      & \textbf{0.000024}                                                   & \textbf{0.000003}                                                     & \textbf{0.121703435}                                                               & 666.328613          & 176.682224            & \textit{0.265157792}              \\
        KM+GAR     & 1.287709                                                            & 0.576568                                                              & 0.447747083                                                                        & 670.487638          & 156.321777            & 0.233146398                       \\
        KM+BF      & 0.013186                                                            & 0.002541                                                              & 0.192707762                                                                        & 670.653112          & 156.392637            & 0.233194529                       \\
        KM+GR      & 0.011910                                                            & 0.001995                                                              & 0.167545233                                                                        & 672.931430          & 159.437076            & 0.236929156                       \\
        KM+CH      & 0.013184                                                            & 0.002048                                                              & 0.155312695                                                                        & 674.160886          & 157.178385            & 0.233146699                       \\
        GAC+GI     & 4.552093                                                            & 1.227828                                                              & 0.269728177                                                                        & 969.678679          & 214.733237            & 0.221447828                       \\
        GACC+GI    & 3.908192                                                            & 0.733851                                                              & 0.187772562                                                                        & 970.224031          & 213.070291            & \textbf{0.219609373}              \\
        KM+GI      & 0.012178                                                            & 0.002108                                                              & 0.173063036                                                                        & \textit{996.233150} & \textit{235.638250}   & 0.23652922
    \end{tabular}
\end{table}
\begin{table}[H]
    \centering
    \caption{Lists average computation time and evaluation for each approach across tests using 15 locations and 4 days}\label{tab:averages-15-locations-4-days}
    \scriptsize
    \begin{tabular}{lllllll}
        Approach   & Computation  & Computation & Computation & Evaluation - $\mu$ & Evaluation - $\sigma$ & Evaluation - $\frac{\sigma}{\mu}$ \\
                   & Time - $\mu$ & Time - $\sigma$ & Time - $\frac{\sigma}{\mu}$ & & & \\
        GAC+GR+BF  & 2.390620                                                            & 0.457114                                                              & 0.191211464                                                                        & \textbf{929.924224}  & 129.695911            & 0.139469333                       \\
        GATG       & 0.999130                                                            & 0.155427                                                              & 0.155562286                                                                        & 931.678599           & 131.730899            & 0.141390925                       \\
        GAC+GR     & 2.387176                                                            & 0.456494                                                              & 0.191227802                                                                        & 932.052914           & 129.772740            & 0.139233233                       \\
        GACC+GR+BF & 2.160390                                                            & 0.434917                                                              & 0.201313923                                                                        & 941.841538           & 130.008533            & 0.138036524                       \\
        GACC+GR    & 2.143543                                                            & 0.434804                                                              & 0.202843494                                                                        & 944.666649           & \textbf{129.641948}   & 0.137235657                       \\
        GITG       & 0.012276                                                            & 0.003757                                                              & 0.306096212                                                                        & 952.964413           & 132.694472            & 0.13924389                        \\
        CH+GI      & 0.008618                                                            & 0.002095                                                              & 0.243065556                                                                        & 959.980725           & 144.641551            & \textit{0.150671308}              \\
        GR+GI      & \textbf{0.000039}                                                   & \textbf{0.000004}                                                     & \textbf{0.104597412}                                                               & 961.133817           & 135.196293            & 0.14066334                        \\
        GAR+GI     & 0.939494                                                            & 0.159025                                                              & 0.169266722                                                                        & 963.440913           & 143.976282            & 0.14943966                        \\
        KM+BF      & \textit{7.332659}                                                   & \textit{31.810776}                                                    & \textit{4.338231859}                                                               & 1113.188018          & 159.945485            & 0.143682363                       \\
        KM+GAR     & 1.684152                                                            & 0.334373                                                              & 0.198540614                                                                        & 1113.690387          & 160.192210            & 0.143839088                       \\
        KM+GR      & 0.013239                                                            & 0.004664                                                              & 0.352271037                                                                        & 1117.856057          & 159.415227            & 0.142608009                       \\
        KM+CH      & 0.016252                                                            & 0.004993                                                              & 0.307194959                                                                        & 1121.260628          & 161.795389            & 0.144297753                       \\
        GACC+GI    & 6.847682                                                            & 0.904047                                                              & 0.132022276                                                                        & 1647.327226          & 225.550233            & \textbf{0.1369189}                \\
        GAC+GI     & 6.735855                                                            & 0.892049                                                              & 0.132432856                                                                        & 1654.194200          & 230.241480            & 0.139186487                       \\
        KM+GI      & 0.013876                                                            & 0.004755                                                              & 0.342677914                                                                        & \textit{1680.691761} & \textit{232.201145}   & 0.138158079
    \end{tabular}
\end{table}
\begin{table}[H]
    \centering
    \caption{Lists average computation time and evaluation for each approach across tests using 25 locations and 7 days}\label{tab:averages-25-locations-7-days}
    \scriptsize
    \begin{tabular}{lllllll}
        Approach   & Computation  & Computation & Computation & Evaluation - $\mu$ & Evaluation - $\sigma$ & Evaluation - $\frac{\sigma}{\mu}$ \\
                   & Time - $\mu$ & Time - $\sigma$ & Time - $\frac{\sigma}{\mu}$ & & & \\
        GAC+GR+BF  & 2.757364                                                            & 0.070118                                                              & 0.025429523                                                                        & \textbf{1224.921655} & 218.453597            & 0.178340873                       \\
        GAC+GR     & 2.752229                                                            & 0.069379                                                              & \textbf{0.025208386}                                                               & 1227.974831          & 219.077690            & 0.178405684                       \\
        GATG       & 1.174132                                                            & 0.065157                                                              & 0.055493493                                                                        & 1249.211698          & 232.957427            & 0.186483546                       \\
        GAR+GI     & 1.145115                                                            & 0.042931                                                              & 0.037490438                                                                        & 1298.771994          & 217.955721            & 0.16781677                        \\
        GITG       & 0.037008                                                            & 0.004152                                                              & 0.112203647                                                                        & 1299.978163          & 229.402565            & 0.176466476                       \\
        GACC+GR+BF & 2.322438                                                            & 0.354714                                                              & 0.152733636                                                                        & 1300.039380          & 256.373114            & 0.197204114                       \\
        GR+GI      & \textbf{0.000055}                                                   & \textbf{0.000010}                                                     & 0.174405584                                                                        & 1303.278191          & 224.211835            & 0.172036819                       \\
        GACC+GR    & 2.171517                                                            & 0.188289                                                              & 0.086708524                                                                        & 1303.379124          & 256.455549            & 0.196762051                       \\
        CH+GI      & 0.023478                                                            & 0.003493                                                              & 0.148782618                                                                        & 1303.547054          & \textbf{216.694963}   & 0.166234861                       \\
        KM+GAR     & 2.473922                                                            & 0.134556                                                              & 0.054389867                                                                        & 1423.636393          & 271.047180            & 0.190390735                       \\
        KM+BF      & 1.697500                                                            & \textit{4.332882}                                                     & \textit{2.55250715}                                                                & 1427.268910          & 282.173377            & \textit{0.197701621}              \\
        KM+GR      & 0.011821                                                            & 0.001488                                                              & 0.125869635                                                                        & 1428.105419          & 272.554303            & 0.190850269                       \\
        KM+CH      & 0.016291                                                            & 0.001898                                                              & 0.116514653                                                                        & 1434.496055          & 272.688511            & 0.190093594                       \\
        GACC+GI    & \textit{11.164482}                                                  & 1.662562                                                              & 0.148915268                                                                        & 2200.445359          & 321.745265            & \textbf{0.146218248}              \\
        GAC+GI     & 9.161882                                                            & 0.358560                                                              & 0.039136028                                                                        & 2233.113133          & 344.559348            & 0.154295518                       \\
        KM+GI      & 0.012839                                                            & 0.001507                                                              & 0.117347705                                                                        & \textit{2261.413558} & \textit{383.340894}   & 0.169513839
    \end{tabular}
\end{table}
\begin{table}[H]
    \centering
    \caption{Lists average computation time and evaluation for each approach across all tests.}
    \label{tab:averages-all-tests}
    \scriptsize
    \begin{tabular}{lllllll}
        Approach   & Computation  & Computation & Computation & Evaluation - $\mu$ & Evaluation - $\sigma$ & Evaluation - $\frac{\sigma}{\mu}$ \\
                   & Time - $\mu$ & Time - $\sigma$ & Time - $\frac{\sigma}{\mu}$ & & & \\
        GAC+GR+BF  & 2.979977                 & 7.530829                    & 2.527143137                             & \textbf{1020.368065} & \textbf{375.291204} & 0.367799833                       \\
        GAC+GR     & 2.449077                 & 0.573792                    & \textbf{0.234288951}                    & 1022.932742        & 376.517470            & 0.368076467                       \\
        GATG       & 1.056100                 & 0.350635                    & 0.332009669                             & 1025.823776        & 377.272585            & 0.367775239                       \\
        GACC+GR+BF & 3.283957                 & 11.213699                   & 3.414691397                             & 1026.018469        & 378.328927            & 0.368735007                       \\
        GACC+GR    & 2.058841                 & 0.552098                    & 0.268159607                             & 1035.318311        & 384.760096            & 0.37163459                        \\
        GITG       & 0.016816                 & 0.013973                    & 0.830951736                             & 1097.052085        & 404.128161            & 0.368376458                       \\
        GAR+GI     & 0.979447                 & 0.291409                    & 0.297524026                             & 1098.753750        & 405.460659            & 0.36901868                        \\
        GR+GI      & \textbf{0.000053}        & \textbf{0.000078}           & 1.472593046                             & 1101.631357        & 403.964025            & 0.366696193                       \\
        CH+GI      & 0.012669                 & 0.010609                    & 0.837414977                             & 1101.948744        & 405.566210            & 0.368044532                       \\
        KM+BF      & \textit{9.931990}        & \textit{35.391964}          & \textit{3.563431295}                    & 1142.732633        & 418.983039            & \textbf{0.366650104}              \\
        KM+GAR     & 1.691711                 & 0.608345                    & 0.359603359                             & 1232.529265        & 461.950473            & 0.374798787                       \\
        KM+GR      & 0.013553                 & 0.005196                    & 0.383363287                             & 1236.909841        & 463.293563            & 0.374557261                       \\
        KM+CH      & 0.017589                 & 0.006696                    & 0.380662466                             & 1243.418740        & 466.350523            & 0.375055087                       \\
        GACC+GI    & 8.228977                 & 3.850029                    & 0.467862454                             & 1792.357060        & 674.690213            & 0.376426231                       \\
        GAC+GI     & 7.738760                 & 3.107706                    & 0.401576755                             & 1802.357683        & 686.223849            & 0.380736773                       \\
        KM+GI      & 0.014386                 & 0.005420                    & 0.376779259                             & \textit{1830.032473} & \textit{701.160152} & \textit{0.383140825}
    \end{tabular}
\end{table}
From analysing these results, there are a few approaches that stand out as being particularly effective.
GAC+GR+BF consistently produces some of the best evaluations across all datasets, while also being relatively fast.
In fact, approaches that utilise genetic algorithms for clustering or trip generation overwhelmingly outperform the
conventional heuristic approaches; on every input with locations greater than 10, genetic algorithms held the top
four spots for route evaluation.
Other approaches of note are GITG, GR+GI and CH+GI, which all find trips within a few hundredths of a second, while
remaining middle of the pack in terms of trip quality.

By far the worst performing approaches are GACC+GI, GAC+GI and KM+GI\@.
The quality of routes produced by the approaches that perform Greedy Insertion Routing are significant outliers amongst
the other approaches, which begs the question as to why this is so.
Logically, one would expect greedy insertion routing to produce a route at least as good and greedy routing, if not better.
It is suggested that further investigation is needed to understand why this is the case, and whether this could be
caused by a
flawed implementation of the greedy insertion algorithm.

Amongst algorithms that start by clustering locations, K-Means Clustering appears to produce significantly worse
routes than those found with genetic approaches.
K-Means approaches are much faster than their genetic counterparts, but this trade off doesn't appear to be worth it
considering that Routing+Insertion approaches are even faster and produce better routes.
Even the K-Means inspired genetic algorithms are outperformed by the standard genetic algorithm approaches,
indicating that these geographic heuristics for clustering do not translate well to producing a good trip.

Further evidence of this is how Convex Hull Routing produces the worst results out of Routing+Insertion approaches.
Convex Hull Routing was included in this project to investigate whether a convex hull could provide a good starting
point for greedy insertion, hopefully being able to speed up the process or produce better results.
While convex hull routing does produce slightly worse results though, it did find routes around 25\% faster than
Greedy Insertion Trip Generation.

It is also worth noting that these geometric based heuristics often produced large coefficients of variation,
indicating that compared to other approaches, different location inputs resulted in a larger difference in the quality
of the routes produced.

The full set of experiment results is available in this project's related gitlab repository, located in
`data\textbackslash results.csv'.