The Multi-Day Trip Planning problem investigated in this project can be simply described like so: given several
locations, and a number of days over which the trip will take place, find a route that visits all locations while
minimising the time spent travelling and distributing time spent evenly across each day.
The motivation behind this problem is centred around tourism and travel, where a user may want to visit several
points of interest in a city or region, and would like to find an efficient route for doing so across a number of days.

This project aims to investigate different potential approaches to solving this problem, and to evaluate the performance
of these approaches against each other.
The structure of this report will be as follows:
\begin{itemize}
    \item In section~\ref{sec:problem-formulation} a mathematical formulation of the Multi-Day Trip Planning problem
    will be introduced.
    \item Section~\ref{sec:literature-review} will examine and analyse existing research into problems similar to
    that covered in this project, and the approaches taken to solve them.
    \item Section~\ref{sec:algorithms-investigated} discusses the algorithms that have been investigated and
    implemented in this project.
    \item Section~\ref{sec:evaluation-and-results} will present the methodology used to evaluate these
    algorithms, and present the results of the experiments ran.
    \item Finally, section~\ref{sec:conclusion-and-future-work} will conclude this report, reviewing the project and
    any future work that could be done.
\end{itemize}\\

\noindent
All the code used in the project is available at: \url{https://git.cs.bham.ac.uk/projects-2024-25/jhl114}.
Code snippets shown in this report are captioned detailing where in the gitlab repository their code can be found.