\subsection{Problem Description}\label{subsec:problem-description}
Given a positive integer $d$ and a graph $G = (V, E)$, where $V$ is set of locations including a designated
starting point $s$ and $E$ is a set of weighted edges linking every location to every other location, find a route
that:
\begin{enumerate}
    \item Visits all nodes $V \setminus c$ once.
    \item Starts and finishes at $s$, having visited it $d$ times, without ever visiting consecutively.
    \item Minimises both the cumulative edge weights in the route and the variance in cumulative weight between
    each visit to $s$.
\end{enumerate}

\subsection{Inputs and Outputs}\label{subsec:inputs-and-outputs}
Inputs:
\begin{itemize}
    \item $d$: The number of times $s$ should be visited in a route.
    Contextually, $d$ represents the number of days a tourist will spend on their trip. $d \in \mathbb{Z}, d > 0$
    \item $G = (V, E)$: A pair comprising:
    \begin{itemize}
        \item[\textbullet] $V$: A set of nodes representing locations the tourist would like to visit.
        $v \in V, v = (x, y, t)$, a triple comprising:
        \begin{itemize}
            \item[\textbullet]$x$: Longitude, indicating the location's geographic east-west position on the
            earth\footnote{\label{latitude-longitude-note}While the coordinates of our locations are
            included in $V$, they are not directly tied to the weight of our edges $E$, which are based on
            time and not distance.}.\\
            $x \in \mathbb{Q}, -180 \leq x \leq 180$.
            \item[\textbullet]$y$: Latitude, indicating the location's geographic north-south position on
            the earth\footnote{See footnote \ref{latitude-longitude-note}}.\\
            $y \in \mathbb{Q}, -90 \leq y \leq 90$.
            \item[\textbullet]$t$: Duration, in minutes, indicating how much time to spend at this location.\\
            $t \in \mathbb{Z}, t > 0$.
        \end{itemize}
        \item[\textbullet] $E$: A set of edges $e \in E$ that connects every node to every other node,
        bidirectionally. $e = (v_1, v_2, w)$, a triple comprising of:
        \begin{itemize}
            \item[\textbullet]$v_1$: A location representing the origin of the edge.\\
            $v_1 \in V$.
            \item[\textbullet]$v_2$: A location representing the destination of the edge.\\
            $v_2 \in V$.
            \item[\textbullet]$w$: A weight indicating the sum of the time it takes to travel from $v_1$ to $v_2$
            and the time the tourist wishes to spent at $v_2$.\\
            $w \in Z, w > 0$.
        \end{itemize}
    \end{itemize}
    \item $s$: Starting point that should be visited $d$ times.
    Contextually, $s$ represents where the tourist is staying and will return to at the end of each day.\\
    $s \in V$.
\end{itemize}
Outputs:
    \begin{itemize}
    \item $R$: A valid route satisfying all constraints, represented as an ordered sequence of locations.\\
    $R = [r_1, r_2, \dots, r_n]$, $r_i \in V$.
\end{itemize}

\subsection{Optimisation}\label{subsec:optimisation}
As previously mentioned in the \hyperref[subsec:problem-description]{Problem Description}, our goal is to find a
route that minimises the cumulative weight and the variance in route weight between each visit to $s$.
To accomplish this the following cost function is applied to each route:
\begin{equation}
    Cost(R) = W \times (1 + \sigma)\label{eq:cost}
\end{equation}
Where $W$ is the sum of the weights of all edges traversed in the route and $\sigma$ is the standard deviation of the
sum of weights between each visit to $s$:
\begin{equation}
    \sigma = \sqrt{\frac{\sum_{i=0}^{d}(x_i-\mu)}{d}}, x_i \in X\label{eq:standard-deviation}
\end{equation}
Where $R$ is divided into sections between each visit to $s$ and $X$ is a list of the sum of weights within these
sections.
$\mu$ is the mean cumulative weight of each $x_i$.\\\\